%-------------------------
% Resume in Latex
% Author : Robert James Gabriel
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoDots}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoDotsSpace}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheadingEducation}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}



\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{https://robertgabriel.ninja/}{\Large Robert James Gabriel}} & Email : \href{mailto:robert\_gabriel@outlook.com}{robert\_gabriel@lookout.com}\\
	\href{https://robertgabriel.ninja}{https://robertgabriel.ninja} & Mobile : +353-85-220-4534 \\
	& \href{https://github.com/RobertJGabriel}{Github}  \href{https://www.linkedin.com/in/robertjamesgabriel/}{Linkedin} \href{https://www.robertgabriel.ninja/apps/}{Apps}  \\
\end{tabular*}



%-----------EXPERIENCE-----------------
\section{\href{https://github.com/RobertJGabriel}{Experience}}
\resumeSubHeadingListStart

\resumeSubheading
{robertgabriel.ninja}{Remote/Traveling}
{Founder / Open source Engineer}{June 2018 - November 2018}
\resumeItemListStart
\resumeItemNoDots{}
{Founded two mico sass company with over 10,000 daily users.
	Worked on opensource tooling Golang and Node modules (5,000 downloads). Created and maintained  apps with over 100,000 daily users. Consulted on projects.}
\resumeItemListEnd


\resumeSubheading
{Teamwork.com}{Cork, Ireland}
{Team Lead/Software Engineer}{January 2015 - May 2018}
\resumeItemListStart
\resumeItemNoDots{}
{Lead the conversion/re-architecture of the Teamwork.com website and platform from Coldfusion to Golang and Jamstack(Knockout), reducing page load times from an average of 5 seconds to an average of fewer than 2 seconds. Developed into a PWA, API endpoints written in Golang and Coldfusion.}
\resumeItemNoDots{}
{Created and architectured modern deployment for changes. Including staging, production, tests, Travis.}
\resumeItemNoDots{}
{Managing a team of four engineers, including time off requests, interviewing potential interns, reviewing code and ensuring the team delivers tasks on time.}
\resumeItemNoDots{}
{Frequently use various services (AWS, S3, Travis, Kubernetes, Lambda, Jest)}    
\resumeItemNoDots{}
{Reduced the time between release to the deployment of application changes from 30 minutes to under 15 minutes by developing the build portion of our continuous integration pipeline using Docker, Kubernetes and Travis.}   
\resumeItemNoDots{}
{Built a microservice used for automated translation of static web pages in pipelines.}   

\resumeItemListEnd

{Software Engineer}
\resumeItemListStart
\resumeItemNoDots{}{ Implemented marketing tools and features within the products, website and blog.}
\resumeItemNoDots{}{
Created a Golang based API documentation generator.}
\resumeItemNoDots{}{
	Developing improvements to an import
system that allows users to import their data from competitors into Teamwork Projects directly.}
\resumeItemNoDots{}{
Responsibilities also included creating PHP, Coldfusion and Golang based server-side/frontend solutions, implemented a signup page used by millions, CSS, Javascript, and SEO implementation.}
      
\resumeItemListEnd

\resumeSubheading
{Engineering Internships}{}
{Microsoft, Dell/EMC, Horner, Teamwork.com}{January 2010 - January 2015}
\resumeItemListStart
\resumeItemNoDotsSpace{Teamwork.com (January 2015 – September 2015)}
{}
\resumeItemNoDotsSpace{Rubicon Center (July 2013 – September 2013)}
{}
\resumeItemNoDotsSpace{Dell/EMC (July 2013 – September 2013)}
{}
\resumeItemNoDotsSpace{Dell/EMC (July 2012 – September 2012) }
{}
\resumeItemNoDotsSpace{Microsoft (February 2011 – March 2011)}
{}
\resumeItemNoDotsSpace{Horner APG (July 2010 – September 2010)}
{}
\resumeItemNoDotsSpace {More details available on \href{robetgabriel.ninja/work}{robetgabriel.ninja/work}}{}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{\href{https://robertgabriel.ninja/education}{Education}}

\resumeSubHeadingListStart
\resumeSubheadingEducation
{Cork Institute of Technology and Science}{Cork, Ireland}
{Bachelor of Honours in Computer Science;  GPA: 3.66}{Aug. 2012 - October. 2016}

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{\href{https://robertgabriel.ninja/projects}{Projects}}
\resumeSubHeadingListStart
\resumeSubItem{Open Source}
{\href{https://www.robertgabriel/apps/helperbird}{OpenDyslexic Chrome} ,
	\href{https://www.robertgabriel/apps/helperbird}{Netflix Hidden Categories},
	\href{https://github.com/yvasiyarov/swagger}{Swagger for Golang},	\href{https://github.com/robertjgabriel/xbox-dvr}{Xbox One DVR}, 	\href{https://github.com/robertjgabriel/Google-profanity-words}{Google profanity words},
	\href{https://www.robertgabriel/apps/helperbird}{More on robertgabriel/apps}.
}
\resumeSubHeadingListEnd


%--------SKILLS------------
\section{\href{https://robertgabriel.ninja}{Skills}}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{Html, Vue.js, Javascript, Vuex , Bem CSS/Sass/Less, Angular, Knockout, PWA, Serverless, Service workers, NPM, Gulp, Webpack, Algorithms, React.js.}
\resumeSubItem{Technologies}{Node.js, Go, Bash, SQL, Firebase, NoSQL, Coldfusion, PHP, Serverless, Express.js, Mongo.DB, AWS, API Design, Git, Babel, Jest, Puppeteer, Electron, Kubernetes, Docker, Coldfront, Netify, Linux and Docker}
\resumeSubHeadingListEnd


%-----------AWARDS-----------------
\section{\href{https://robertgabriel.ninja/awards}{Awards}}
\resumeSubHeadingListStart
\resumeSubItem{Awards}{11 Engineering awards, 8 workplace awards, 5 Scholar awards and 3 grant awards}
\resumeSubItem{Papers}{\href{https://www.robertgabriel.ninja/research-into-web-accessibility-for-dyslexics}{Web accessibility an Dyslexics},  \href{https://www.robertgabriel.ninja/adblockers}{Problems Posed by Ad-blockers},  \href{https://www.robertgabriel.ninja/adblockers}{Invited to speak at three conferences.}	}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
